SAT Solving for Vesicle Traffic Systems in Cells

### 2017-06-20 paper/experiments.tex
exp

We have implemented the encoding of the constraints
in the python interface of $\zthree$.
%
Our implementation supports several versions of the
models of vesicle traffic systems.
\todo{describe the variations}

\begin{enumerate}[label=\Alph*]
\item Every present molecule is considered to be active.
\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules. 
\item Activity of molecules on the edges is based on Boolean function of presence of other molecules
\item Activity of molecules both on the edges and nodes is based on Boolean function of presence of other molecules.
\item Activity of molecules on the edges is driven by pairing inhibition.
\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition.
\item Version F with additional constraint that every edge is distinct.
%\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition with every edge is distinct.
%\item Activity of molecules on the nodes is based on Boolean function of presence of other moleculess and on edge by pairing inhibition with self-edges are allowed.
\item Version F but self-edges are allowed.
\end{enumerate}
%
Our tool allows user to choose a model and the size of
the network.
%
It builds the needed constraints and applies $\zthree$
on the constraints.
%
Our tool also translates the model found by $\zthree$
into a vesicle traffic system and presents a visual
output to the user.

We have applied the tool for the above variations
for searching the vesicle traffic systems that satisfies
their corresponding properties.

>>>>

We have implemented the encoding of the constraints
in the python interface of $\zthree$. Basic idea is to constraint the variables such that vesicular transport rules are respected and using constraints (D0-D5) connect this system with the connectivity of the underlying structure (graph). We are interested in both least connectivity that is required for a vesicular transport version to work and least connectivity that guarantees that vesicular transport system with that connectivity will always satisfies the rules.

% Whether a valid vesicular transport system is of certain connectiviity.   
After creating the formula we ship them directly to the solver without any additional overhead. Besides using the default Z3 solvers we have used for these experiments \ankit{Z3, picoSAT, Lingeling}. The performance of Z3 was ...
%
Our implementation supports several versions of the
models of vesicle traffic systems listed in Table 2. Starting from most basic model  \Ankit{add...}
\todo{describe the variations}

\begin{enumerate}[label=\Alph*]
\item Every present molecule is considered to be active.
\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules. 
\item Activity of molecules on the edges is based on Boolean function of presence of other molecules
\item Activity of molecules both on the edges and nodes is based on Boolean function of presence of other molecules.
\item Activity of molecules on the edges is driven by pairing inhibition.
\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition.
\item Version F with additional constraint that every edge is distinct.
%\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition with every edge is distinct.
%\item Activity of molecules on the nodes is based on Boolean function of presence of other moleculess and on edge by pairing inhibition with self-edges are allowed.
\item Version F but self-edges are allowed.
\end{enumerate}
%
Our tool allows user to choose a model and the size of
the network besides other parameters like connectivity and number of parallel edges. 
%
Our tool uses Z3 python interface to build the needed constraints and applies $\zthree$
on the constraints. \Ankit{In other solver variations ...}
%
Our tool also translates the model found by $\zthree$
into a vesicle traffic system and presents a visual
output to the user. The graph provides an overview of the vesicle transport system with directed labeled edges and nodes providing the complete information about the shown graph. The output graph will satisfy the underlying rules of the system, so it is a valid vesicle transport network.

We have applied the tool for the above variations for searching the vesicle traffic systems that satisfies
their corresponding properties. In case the solver finds an satisfying assignment to the generated formula i
